### 2016-09-03 MSR-design.tex
Add MSBR cross section figures.

\documentclass{article}
\setlength{\parindent}{0pt}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{cleveref}

\graphicspath{{./figures/}}

\begin{document}
\section{Comprehensive, expensive (3D) models}
\subsection{MSBR}

The most detailed report on ORNL's molten salt breeder reactor is the technical
report by Robertson. \cite{robertson1971conceptual} A nice overview of the MSBR
geometry is shown in \cref{fig:vertical,fig:horizontal,fig:zoom_horiz}.

\begin{figure}[htpb]
  \centering
  \includegraphics{vertical_MSBR_cross_section.png}
  \caption{Vertical cross section of MSBR.}
  \label{fig:vertical}
\end{figure}
\begin{figure}[htpb]
  \centering
  \includegraphics{horizontal_MSBR_cross_section.png}
  \caption{Horizontal cross section of MSBR.}
  \label{fig:horizontal}
\end{figure}
\begin{figure}[htpb]
  \centering
  \includegraphics{zoomed_horizontal_MSBR_cross_section.png}
  \caption{Zoomed in horizontal cross-section of MSBR. Shows presence of
    interstitials between graphite block elements in zone 1 of the reactor.}
  \label{fig:zoom_horiz}
\end{figure}

\section{Simplified models}
\subsection{MSBR children}
\subsubsection{Cammi et. al.}
This model is based on the multi-physics model by \cite{cammi2011multi}.

\bibliographystyle{unsrt}
\bibliography{MSR-design}
\end{document}

### 2016-09-06 MSR-design.tex
Change references to match new bib in tex file.

@@
 \usepackage{cleveref}
-
 \graphicspath{{./figures/}}
@@
 \begin{document}
+
 \section{Comprehensive, expensive (3D) models}
+
 \subsection{MSBR}
@@
 The most detailed report on ORNL's molten salt breeder reactor is the technical
-report by Robertson. \cite{robertson1971conceptual} A nice overview of the MSBR
-geometry is shown in \cref{fig:vertical,fig:horizontal,fig:zoom_horiz}.
+report by Robertson. \cite{robertson_conceptual_1971} A nice overview of the
+MSBR geometry is shown in \cref{fig:vertical,fig:horizontal,fig:zoom_horiz}.
 
@@
 \section{Simplified models}
+
 \subsection{MSBR children}
+
 \subsubsection{Cammi et. al.}
-This model is based on the multi-physics model by \cite{cammi2011multi}.
+
+This model is based on the multi-physics model by
+\cite{cammi_multi-physics_2011}.
 

### 2016-09-07 MSR-design.tex
Add history and revise bibliography structure.

@@
 \usepackage{cleveref}
+\usepackage{textcomp}
+\usepackage{placeins}
 \graphicspath{{./figures/}}
 
+\title{Advanced Reactor Fuel cycle Molten Salt Reactor Design}
+\author{Alexander Lindsay, Katy Huff} % As you author additions/changes, add
+                                      % your name here!!!
+
 \begin{document}
+\maketitle
+
+\section{Brief History}
+
+The basis for this quick synopsis comes from
+\cite{wiki:Molten_salt_reactor}. Research into molten salt reactors (MSRs) began
+in earnest with the Aircraft Reactor Experiment (ARE), with experiments shared
+between Oak Ridge National Lab (ORNL) and what is now Idaho National Lab
+(INL). The ARE used NaF-ZrF$_4$-UF$_4$ (53-41-6 mol\%) as fuel. The reactor was
+moderated by beryllium oxide (BeO), used liquid sodium as the secondary coolant,
+and had a peak tempeature around 860 \textdegree C. The ARE managed to generate
+100 MWh over the course of nine days in 1954. There was another reactor that
+went critical at ORNL in 1957 called the Pratt and Whitney Aircraft Reactor-1
+(PWAR-1). Although it produced essentially no power, the PWAR-1 is still one of
+only three critical MSRs ever built.
+
+The most successful MSR was the Molten-Salt Reactor Experiment (MSRE) which went
+critical in 1965 and operated for four years at ORNL. The MSRE fuel was
+LiF-BeF$_2$-ZrF$_4$-UF$_4$ (65-29-5-1 mol\%) with graphite core moderation. The
+secondary coolant was 2LiF-BeF$_2$ (also known as FLiBe). Operating temperatures
+went as high as 650 \textdegree C. MSRE neutronics were meant to mimic that of
+an epithermal thorium molten salt breeder reactor (MSBR); however, for the MSRE
+the expensive breeding blanket was sacrificed in favor of neutron
+measurements. At full design power, the MSRE operated at 7.4 MW$_{th}$. Over the
+course of the late 1960s the MSRE operated at full capacity for an equivalent of
+1.5 years.
+
+The logical follow-on from the MSRE was the MSBR; however, the MSBR was never
+constructed. Funding for the MSR program was cut in favor of the liquid metal
+fast-breeder reactor (LMFBR) program. Consequently, as of today, the ARE,
+PWAR-1, and MSRE are the only critical MSRs ever operated.
 
 \section{Comprehensive, expensive (3D) models}
+
+\subsection{MSRE}
 
@@
 
+\FloatBarrier
+
 \bibliographystyle{unsrt}

### 2016-09-15 MSR-design.tex
Add MSRE reactor vessel.
Detailing neutronics and hydraulics in Kophazi article.

@@
 \usepackage{placeins}
+\usepackage[T1]{fontenc}
+\usepackage{gensymb}
+\usepackage[utf8]{inputenc}
 \graphicspath{{./figures/}}
@@
                                       % your name here!!!
+
+% To do: Decide how to present figures in a way that they don't have both our
+% figure labels as well as the original documents; also make sure we are
+% reproducing those figures in an ethical way
 
@@
 
-\section{Comprehensive, expensive (3D) models}
+\section{MSRE}
 
-\subsection{MSRE}
+\subsection{Salt properties}
 
-\subsection{MSBR}
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[width=\textwidth]{salt_properties.png}
+  \caption{Composition and properties of fuel, flush, and coolant
+    salts. \cite{robertson_msre_1965}}
+  \label{fig:salt_properties}
+\end{figure}
+
+\subsection{Layout \& Equipment}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{flow_diagram.png}
+  \caption{Macroscopic layout of the MSRE \cite{robertson_msre_1965}}
+  \label{fig:MSRE_layout}
+\end{figure}
+
+\subsubsection{Reactor vessel}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{MSRE_reactor_vessel.png}
+  \caption{MSRE reactor vessel. \cite{robertson_msre_1965}}
+  \label{fig:MSRE_reactor}
+\end{figure}
+
+\subsection{Reactivity considerations}
+
+The MSRE has a negative temperature coefficient of 6.4 - 9.9 x $10^{-5}$
+($\Delta$k/k)/\textdegree F depending on the choice of
+fuel. \cite{robertson_msre_1965} The MSRE's three control rods have a combined
+worth of 5.6 - 7.6 \% $\Delta$k/k, again depending on the
+fuel. \cite{robertson_msre_1965}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{reactivity-losses.png}
+  \caption{Losses in reactivity associated with different
+    phenomena. \cite{robertson_msre_1965}}
+  \label{fig:reactivity_losses}
+\end{figure}
+
+\section{MSRE adaption for modelling}
+
+\subsection{Kophazi article review}
+
+Kophazi developed a 3D time-dependent simulation that was validated against MSRE
+data. \cite{kophazi_development_????} The model consists of a conventional
+neutronics model extended to deal with the precursor drift that is unique to
+MSRs and the core's thermal behavior. The thermal model includes the true
+geometry of the fuel channels as well as the moderator connecting them. Salt
+flow is assumed to be only in the reactor's axial direction, which reduces the
+number of non-linear variables that have to be solved for.
+
+\subsubsection{Neutronics}
+
+Neutrons are described with time-dependent multi-group diffusion theory as shown
+in \cref{eq:neutrons}:
+
+\begin{equation}
+\frac{1}{v_g}\frac{\partial \phi_g}{\partial t} - \nabla \cdot D_g \nabla \phi_g
++ \Sigma_g^r \phi_g = \sum_{g \ne g'}^G \Sigma_{g'\rightarrow g}^s \phi_{g'} + \chi_g^p \sum_{g' = 1}^G (1 - \beta)
+\nu \Sigma_{g'}^f \phi_{g'} + \sum_i^I \lambda_i \chi_g^{d,i} C_i
+\label{eq:neutrons}
+\end{equation}
+
+Delayed neutron pre-cursors are described by \cref{eq:precursors}:
+
+\begin{equation}
+\frac{\partial C_i}{\partial t} = \sum_{g'= 1}^G \beta_i \nu \Sigma_{g'}^f
+\phi_{g'} - \lambda_i C_i - \frac{\partial}{\partial z} u C_i
+\label{eq:precursors}
+\end{equation}
+
+with the last term representing the effect of fuel advection. In
+\cite{kophazi_development_????}, \cref{eq:neutrons} is solved only in the
+reactor core, whereas \cref{eq:precursors} is solved both in the core and in the
+MSRE external primary circuit. The external loop is modeled as a single pipe
+with a volume equal to the total volume of all the external components and
+pipelines of the primary circuitry. \cite{kophazi_development_????} It is not
+entirely clear how pipe cross sectional areas are handled, which would determine
+the transit times of individual pieces of fluid and subsequently the
+distribution of delayed neutron production in the external primary circuit. That
+is a piece that would likely need to be included in detailed ARFC accident
+models.
+
+As pointed out in \cite{kophazi_development_????}, it is not possible to solve
+\cref{eq:neutrons,eq:precursors} on the same mesh. \Cref{eq:neutrons} needs to
+be solved over the entire reactor cross-section including fuel channels and the
+graphite moderator in between, whereas \cref{eq:precursors} is only applicable
+within the fuel channels. Kophazi solves this issue by introducing a fuel
+fraction parameter, $p_f$, and creating effective fuel flow
+channels. \Cref{fig:kophazi_homo} shows how Kophazi transforms the MSRE unit
+cell into neutronic and precursor elements. The number of effective fuel
+channels in the unit cell is determined by the refinement of the neutron grid,
+e.g. the \# of channels is equivalent to the number of neutronic elements in a
+given MSRE unit cell. Consequently, once the domain is discretized (Kophazi uses
+the finite volume method), the delayed neutron source term (last term in
+\cref{eq:neutrons}) is multiplied by the fuel fraction $p_f$. Homogenization of
+the removal, scattering, and fission cross sections allows translation of the
+model from the real to effective geometry. Details of the discretization can be
+found in \cite{kophazi_development_????}.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{kophazi_neutronics_discretization.png}
+  \caption{Homogenized model of fuel channels \cite{kophazi_development_????}}
+  \label{fig:kophazi_homo}
+\end{figure}
+
+\subsubsection{Thermal hydraulics}
+
+Temperature in the fuel is determined by a 1-D convection model in the axial
+direction. Moderator temperatures are calculated with a 3-D conduction
+model. Coupling between the moderator and fuel temperatures is accomplished
+through an axially varying heat transfer coefficient calculated with a Nusselt
+correlation; see \cite{kophazi_development_????} for details of the Nusselt
+correlation. Thermal expansion of the fuel was not accounted for while
+determining the reactor temperature profile; however, expansion is considered
+when determining homogenized neutron cross-sections.
+
+\section{MSBR}
 

### 2016-09-18 MSR-design.tex
Add Cammi's model simplifications into the Latex file
Adds a figure about boundary conditions of Cammi's model

@@
 \title{Advanced Reactor Fuel cycle Molten Salt Reactor Design}
-\author{Alexander Lindsay, Katy Huff} % As you author additions/changes, add
+\author{Alexander Lindsay, Katy Huff, Andrei Rykhlevskii} % As you author additions/changes, add
                                       % your name here!!!
@@
 
+Model's simplifications:
+\begin{enumerate}
+	\item Considered only one channel (diameter ~0.05 m)
+	\item Hollow cylinder instead of block with a hole (with keeping the same fuel to graphite ratio) 
+	\item Infinite length of the channel (z tends to infinity)
+\end{enumerate}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{Cammi_simplification_1.png}
+  \caption{Cammi's simplification of MSBR's geometry. \cite{cammi_multi-physics_2011}}
+  \label{fig:simlification}
+\end{figure}
+
+Neutronics Boundary Conditions.
+\begin{enumerate}
+	\item \textit{Inlet boundary}.
+The "vacuum" condition is adopted for the fast and thermal neutron fluxes.
+The circulation of delayed neutron precursors is taken into account considering that a certain amount of DNPs can return into the core from the external loop:
+
+	\[ C_{i,in}(t) = C_{i,out}(t- \tau_{EL})exp(- \lambda_i \tau_{EL}) \]
+	\item \textit{Outlet boundary}. "Vacuum" condition for fast and thermal neutrons.  
+	\item \textit{Wall and central boundaries.} Symmetry boundary conditions are imposed for the neutron fluxes at r=0 and $ r=R_2 $.
+\end{enumerate}
+
+Flow and heat transfer boundary conditions.
+\begin{enumerate}
+	\item \textit{Inlet boundary}.
+The inlet velocity is given as $u_z = U_{in}=1.47 m/s$ and $u_r=0$.
+Turbulent kinetic energy $k_{in}=0.007 m^2/s^2$.
+Turbulent dissipation rate $\epsilon_{in}=0.033 m^2/s^2 $.
+$T_F=T_in=839K$.
+	\item \textit{Outlet boundary}. The "local one-way method" is exploited for u,k,$\epsilon$, and $T_F$.
+	\item \textit{Central boundaries.} Symmetry conditions are considered on the axis of the channel.
+	\item \textit{Wall and central boundaries.} "Wall function approach" that use empirically-based relations in turbulent flows near solid boundaries in order to describe the velocity and temperature profile in the thin boundary layer near the wall, instead of solving the turbulence equations.
+\end{enumerate}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics{Cammi_simplification_2.png}
+  \caption{(b) Fluid flow and heat transfer boundary conditions; (c) neutron flux and DNP boundary conditions. \cite{cammi_multi-physics_2011}}
+  \label{fig:simlification-2}
+\end{figure}
+
 \FloatBarrier

### 2016-09-20 MSR-design.tex
Finish review of Kophazi article.

@@
 \usepackage[utf8]{inputenc}
+\usepackage{caption}
+\usepackage[export]{adjustbox}
 \graphicspath{{./figures/}}
+
+\let\Oldsection\section
+\renewcommand{\section}{\FloatBarrier\Oldsection}
+
+\let\Oldsubsection\subsection
+\renewcommand{\subsection}{\FloatBarrier\Oldsubsection}
+
+\let\Oldsubsubsection\subsubsection
+\renewcommand{\subsubsection}{\FloatBarrier\Oldsubsubsection}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{salt_properties.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{salt_properties.png}
   \caption{Composition and properties of fuel, flush, and coolant
@@
   \centering
-  \includegraphics{flow_diagram.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{flow_diagram.png}
   \caption{Macroscopic layout of the MSRE \cite{robertson_msre_1965}}
@@
 
+A cutaway diagram of the MSRE reactor is shown in \cref{fig:MSRE_reactor}. Fuel
+enters through the inlet and is distributed evenlgy along the outside of the
+reactor vessel in a small annular region of 1 inch
+width. \cite{robertson_msre_1965} The fluid fuel then flows turbulently
+downward, cooling the reactor vessel to within 5\textdegree F of the entering
+bulk salt temperature (1175 \textdegree F). \cite{robertson_msre_1965} Some MSRE
+modeling papers (\cite{kophazi_development_????}) refer to this down-flowing
+region as the \textit{downcomer}. The fuel salt is collected in the lower plenum
+(lower \textit{space}) of the reactor where straightening vanes remove the
+salt's rotational motion. The salt then flows upward through approximately 1140
+0.4-inch by 1.2-inch fuel channels that are formed by machinging grooves in the
+sides of the graphite moderator columns \cite{robertson_msre_1965}; these are the
+regions where fission occurs. The graphite columns themselves have 2-inch by
+2-inch square cross sections. Nominal core volume is 90 ft$^3$, with 70 ft$^3$
+occupied by graphite and 20 ft$^3$ occupied by fuel. \cite{robertson_msre_1965}
+After flowing through the core channels, the fuel collects in the upper plenum
+before exiting through the outlet.
+
 \begin{figure}[htpb]
   \centering
-  \includegraphics{MSRE_reactor_vessel.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{MSRE_reactor_vessel.png}
   \caption{MSRE reactor vessel. \cite{robertson_msre_1965}}
@@
 \end{figure}
+
+Though studies were conducted with the MSRE core surrounded by varying
+thicknesses of reflector \cite{haubenreich_msre_1964}, the experimental design
+was bare. This type of reactor design lends itself most naturally to a vacuum
+boundary condition for neutrons (zero incoming flux) like that used in
+\cite{dulla_neutron_2004}.
 
@@
   \centering
-  \includegraphics{reactivity-losses.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{reactivity-losses.png}
   \caption{Losses in reactivity associated with different
@@
 model from the real to effective geometry. Details of the discretization can be
-found in \cite{kophazi_development_????}.
+found in \cite{kophazi_development_????}. Unfortunately, neither
+\cite{kophazi_development_????} or cited references for the DALTON code,
+describe the boundary conditions used for neutrons.
 
@@
   \centering
-  \includegraphics{kophazi_neutronics_discretization.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{kophazi_neutronics_discretization.png}
   \caption{Homogenized model of fuel channels \cite{kophazi_development_????}}
@@
 
-\subsubsection{Thermal hydraulics}
+\subsubsection{Thermal Hydraulics}
 
@@
 determining the reactor temperature profile; however, expansion is considered
-when determining homogenized neutron cross-sections.
+($\kappa = 0.57 mg/cm^3 K$) when determining homogenized neutron
+cross-sections. A model for the heat exchanger is included with a heat sink term
+proportional to the temperature difference between fuel and coolant salts, with
+the constant of proportionality determined from steady-state MSRE operational
+data. With the exception of the heat exchanger, the thermal code assumes zero
+heat flux boundary conditions.
+
+\subsubsection{Reactor Model}
+
+Cell weighting and cross section homogenization calculations were carried out
+using SCALE. In order to work with the 1D nature of the SCALE/CSAS/XSDRN code,
+the actual MSRE geometry was simplified as shown in \cref{fig:real-vs-model}
+where the actual geometry is on the left and the model geometry is on the
+right. Note that the far left sub-figure of \cref{fig:kophazi_homo} is the
+zoomed, unit cell version of the left sub-figure of \cref{fig:real-vs-model}.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{kophazi-actual-vs-model-core-geometry.png}
+  \caption{Left figure shows snapshot of actual MSRE core geometry; to satisfy
+    the 1D SCALE/CSAS/XSDRN code, the more regular geometry in the right figure
+    is used \cite{kophazi_development_????}}
+  \label{fig:real-vs-model}
+\end{figure}
+
+Neutron cross sections were collapsed into eight energy groups, distributed
+evenly on a logarithmic scale, with additional groups added in resonance and
+thermal regions. Control rods were modeled with albedo boundary conditions for
+thermal neutrons. More control rod modeling details can be found in
+\cite{kophazi_development_????}.
+
+Neutron and thermal calculations are performed on separate grids. The axial and
+horizontal neutron grids are both shown in \cref{fig:neutron-grid}. It includes
+regions for the lower and upper salt plena, downcomer, and three control rods. A
+section of the horizontal thermal grid is shown in \cref{fig:thermal-grid}. In
+general, the thermal grid is finer than the neutron grid. Thermal and neutronic
+calculations are coupled in the following way. Each cell of the neutron mesh
+(containing both fuel and moderator, recall \cref{fig:kophazi_homo}) is
+considered to have uniform cross-sections. To generate these constant
+cross-sections in each neutronic cell, the fine-mesh temperature fields from
+the thermal calculation (called THERM) are spatially averaged using an auxiliary
+program. This averaged neutron-cell-specific temperature is then used in
+conjunction with cross section interpolation tables generated by SCALE to
+determine the macroscopic cross sections for each neutron cell in the
+simulation.
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{3d-neutron-grid.png}
+  \caption{Grid for cross section homogenization and neutron cross sections
+    \cite{kophazi_development_????}}
+  \label{fig:neutron-grid}
+\end{figure}
+
+\begin{figure}[htpb]
+  \centering
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{cross-section-of-thermal-grid.png}
+  \caption{Cross-section of thermal grid \cite{kophazi_development_????}}
+  \label{fig:thermal-grid}
+\end{figure}
+
+Feedback from the neutron to thermal calculations is accomplished by translating
+the power distribution from the coarse neutron grid to the fine thermal grid
+using another auxiliary program. This power distribution is then used as a heat
+source in the thermal code.
 
@@
   \centering
-  \includegraphics{vertical_MSBR_cross_section.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{vertical_MSBR_cross_section.png}
   \caption{Vertical cross section of MSBR.}
@@
   \centering
-  \includegraphics{horizontal_MSBR_cross_section.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{horizontal_MSBR_cross_section.png}
   \caption{Horizontal cross section of MSBR.}
@@
   \centering
-  \includegraphics{zoomed_horizontal_MSBR_cross_section.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{zoomed_horizontal_MSBR_cross_section.png}
   \caption{Zoomed in horizontal cross-section of MSBR. Shows presence of

### 2016-09-20 MSR-design.tex
Reduce width of Cammi boundary condition figure.
Add ARFC MSRE reactor design step list.

@@
 
-\title{Advanced Reactor Fuel cycle Molten Salt Reactor Design}
+\newcommand{\code}[1]{\texttt{#1}}
+
+\title{Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design}
 \author{Alexander Lindsay, Katy Huff, Andrei Rykhlevskii} % As you author additions/changes, add
@@
 
+\subsection{ARFC MSRE Model Design Plan}
+
+\begin{enumerate}
+\item Test whether \code{gmsh} can generate heterogeneous 3D mesh structure
+  like that in the actual MSRE geometry.
+\item For expected range of temperatures and some defined sequence of
+  temperature step sizes, generate table of few-group neutronics cross sections
+  with \code{SERPENT}.
+  \begin{itemize}
+    \item If \code{gmsh}, or that failing \code{cubit}, is capable of generating
+      heterogeneous grid, we can generate unique cross regions for each region
+    \item If we cannot generate heterogeneous grid, we will have to homogenize
+      the cross sections similar to what is done in
+      \cite{kophazi_development_????}.
+  \end{itemize}
+\item Armed with tables for quick interpolation of cross sections, we should be
+  able to perform coupled calculations for neutron density and
+  temperature.
+  \begin{itemize}
+    \item As a first pass, the fuel salt flow velocity can be a user input as
+      opposed to a non-linear variable that is a function of temperature.
+    \item We will need to decide whether neutron and temperature calculations
+      should be performed on the same grid, and in transient calculations
+      whether those two fields should be updated on the same step-size.
+      \begin{itemize}
+        \item If not using the same grid and/or step-size, the neutronic and
+          temperature calculations will need to be split into their own
+          applications and coupling will have to be performed using the MOOSE
+          multi-app system.
+      \end{itemize}
+  \end{itemize}
+\end{enumerate}
+
 \section{MSBR}
@@
   \centering
-  \includegraphics{Cammi_simplification_1.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{Cammi_simplification_1.png}
   \caption{Cammi's simplification of MSBR's geometry. \cite{cammi_multi-physics_2011}}
@@
   \centering
-  \includegraphics{Cammi_simplification_2.png}
+  \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{Cammi_simplification_2.png}
   \caption{(b) Fluid flow and heat transfer boundary conditions; (c) neutron flux and DNP boundary conditions. \cite{cammi_multi-physics_2011}}

### 2016-10-04 MSR-design.tex
spellcheck

@@
 moderated by beryllium oxide (BeO), used liquid sodium as the secondary coolant,
-and had a peak tempeature around 860 \textdegree C. The ARE managed to generate
+and had a peak temperature around 860 \textdegree C. The ARE managed to generate
 100 MWh over the course of nine days in 1954. There was another reactor that
@@
 A cutaway diagram of the MSRE reactor is shown in \cref{fig:MSRE_reactor}. Fuel
-enters through the inlet and is distributed evenlgy along the outside of the
+enters through the inlet and is distributed evenly along the outside of the
 reactor vessel in a small annular region of 1 inch
@@
 salt's rotational motion. The salt then flows upward through approximately 1140
-0.4-inch by 1.2-inch fuel channels that are formed by machinging grooves in the
+0.4-inch by 1.2-inch fuel channels that are formed by machining grooves in the
 sides of the graphite moderator columns \cite{robertson_msre_1965}; these are the

### 2016-10-04 MSR-design.tex
adds acronym capability. no more keeping track of whether you've spell it out already. add new acronyms to the acros.tex file and use them in the text with \gls{ACRO}. It'll auto-expand on first use. Plurality is handled with \glspl

@@
 \graphicspath{{./figures/}}
+
+\usepackage[acronym,toc]{glossaries}
+\include{acros}
+\makeglossaries
 
@@
 
-The basis for this quick synopsis comes from
-\cite{wiki:Molten_salt_reactor}. Research into molten salt reactors (MSRs) began
-in earnest with the Aircraft Reactor Experiment (ARE), with experiments shared
-between Oak Ridge National Lab (ORNL) and what is now Idaho National Lab
-(INL). The ARE used NaF-ZrF$_4$-UF$_4$ (53-41-6 mol\%) as fuel. The reactor was
-moderated by beryllium oxide (BeO), used liquid sodium as the secondary coolant,
-and had a peak temperature around 860 \textdegree C. The ARE managed to generate
+The basis for this quick synopsis comes from \cite{wiki:Molten_salt_reactor}. 
+Research into \glspl{MSR} began in earnest with the \gls{ARE}, with experiments 
+shared between \gls{ORNL} and what is now \gls{INL}. The \gls{ARE} used 
+NaF-ZrF$_4$-UF$_4$ (53-41-6 mol\%) as fuel. The reactor was moderated by 
+beryllium oxide (BeO), used liquid sodium as the secondary coolant, and had a 
+peak temperature around 860 \textdegree C. The \gls{ARE} managed to generate
 100 MWh over the course of nine days in 1954. There was another reactor that
-went critical at ORNL in 1957 called the Pratt and Whitney Aircraft Reactor-1
+went critical at \gls{ORNL} in 1957 called the Pratt and Whitney Aircraft Reactor-1
 (PWAR-1). Although it produced essentially no power, the PWAR-1 is still one of
@@
 
-The most successful MSR was the Molten-Salt Reactor Experiment (MSRE) which went
-critical in 1965 and operated for four years at ORNL. The MSRE fuel was
+The most successful \gls{MSR}was the \gls{MSRE} which went
+critical in 1965 and operated for four years at \gls{ORNL}. The \gls{MSRE} fuel was
 LiF-BeF$_2$-ZrF$_4$-UF$_4$ (65-29-5-1 mol\%) with graphite core moderation. The
 secondary coolant was 2LiF-BeF$_2$ (also known as FLiBe). Operating temperatures
-went as high as 650 \textdegree C. MSRE neutronics were meant to mimic that of
-an epithermal thorium molten salt breeder reactor (MSBR); however, for the MSRE
+went as high as 650 \textdegree C. \gls{MSRE} neutronics were meant to mimic that of
+an epithermal thorium molten salt breeder reactor (MSBR); however, for the \gls{MSRE}
 the expensive breeding blanket was sacrificed in favor of neutron
-measurements. At full design power, the MSRE operated at 7.4 MW$_{th}$. Over the
-course of the late 1960s the MSRE operated at full capacity for an equivalent of
+measurements. At full design power, the \gls{MSRE} operated at 7.4 MW$_{th}$. Over the
+course of the late 1960s the \gls{MSRE} operated at full capacity for an equivalent of
 1.5 years.
 
-The logical follow-on from the MSRE was the MSBR; however, the MSBR was never
-constructed. Funding for the MSR program was cut in favor of the liquid metal
-fast-breeder reactor (LMFBR) program. Consequently, as of today, the ARE,
-PWAR-1, and MSRE are the only critical MSRs ever operated.
+The logical follow-on from the \gls{MSRE} was the MSBR; however, the MSBR was never
+constructed. Funding for the \gls{MSR}program was cut in favor of the
+\gls{LMFBR} program. Consequently, as of today, the \gls{ARE},
+PWAR-1, and \gls{MSRE} are the only critical MSRs ever operated.
 
-\section{MSRE}
+\section{\gls{MSRE}}
 
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{flow_diagram.png}
-  \caption{Macroscopic layout of the MSRE \cite{robertson_msre_1965}}
+  \caption{Macroscopic layout of the \gls{MSRE} \cite{robertson_msre_1965}}
   \label{fig:MSRE_layout}
@@
 
-A cutaway diagram of the MSRE reactor is shown in \cref{fig:MSRE_reactor}. Fuel
+A cutaway diagram of the \gls{MSRE} reactor is shown in \cref{fig:MSRE_reactor}. Fuel
 enters through the inlet and is distributed evenly along the outside of the
@@
 downward, cooling the reactor vessel to within 5\textdegree F of the entering
-bulk salt temperature (1175 \textdegree F). \cite{robertson_msre_1965} Some MSRE
+bulk salt temperature (1175 \textdegree F). \cite{robertson_msre_1965} Some \gls{MSRE}
 modeling papers (\cite{kophazi_development_????}) refer to this down-flowing
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{MSRE_reactor_vessel.png}
-  \caption{MSRE reactor vessel. \cite{robertson_msre_1965}}
+  \caption{\gls{MSRE} reactor vessel. \cite{robertson_msre_1965}}
   \label{fig:MSRE_reactor}
@@
 
-Though studies were conducted with the MSRE core surrounded by varying
+Though studies were conducted with the \gls{MSRE} core surrounded by varying
 thicknesses of reflector \cite{haubenreich_msre_1964}, the experimental design
@@
 
-The MSRE has a negative temperature coefficient of 6.4 - 9.9 x $10^{-5}$
+The \gls{MSRE} has a negative temperature coefficient of $6.4 - 9.9 \times10^{-5}$
 ($\Delta$k/k)/\textdegree F depending on the choice of
-fuel. \cite{robertson_msre_1965} The MSRE's three control rods have a combined
+fuel. \cite{robertson_msre_1965} The \gls{MSRE}'s three control rods have a combined
 worth of 5.6 - 7.6 \% $\Delta$k/k, again depending on the
@@
 
-\section{MSRE adaption for modelling}
+\section{\gls{MSRE} adaption for modelling}
 
@@
 
-Kophazi developed a 3D time-dependent simulation that was validated against MSRE
+Kophazi developed a 3D time-dependent simulation that was validated against \gls{MSRE}
 data. \cite{kophazi_development_????} The model consists of a conventional
@@
 
-Delayed neutron pre-cursors are described by \cref{eq:precursors}:
+Delayed neutron precursors are described by \cref{eq:precursors}:
 
@@
 reactor core, whereas \cref{eq:precursors} is solved both in the core and in the
-MSRE external primary circuit. The external loop is modeled as a single pipe
+\gls{MSRE} external primary circuit. The external loop is modeled as a single pipe
 with a volume equal to the total volume of all the external components and
@@
 fraction parameter, $p_f$, and creating effective fuel flow
-channels. \Cref{fig:kophazi_homo} shows how Kophazi transforms the MSRE unit
+channels. \Cref{fig:kophazi_homo} shows how Kophazi transforms the \gls{MSRE} unit
 cell into neutronic and precursor elements. The number of effective fuel
@@
 e.g. the \# of channels is equivalent to the number of neutronic elements in a
-given MSRE unit cell. Consequently, once the domain is discretized (Kophazi uses
+given \gls{MSRE} unit cell. Consequently, once the domain is discretized (Kophazi uses
 the finite volume method), the delayed neutron source term (last term in
@@
 proportional to the temperature difference between fuel and coolant salts, with
-the constant of proportionality determined from steady-state MSRE operational
+the constant of proportionality determined from steady-state \gls{MSRE} operational
 data. With the exception of the heat exchanger, the thermal code assumes zero
@@
 using SCALE. In order to work with the 1D nature of the SCALE/CSAS/XSDRN code,
-the actual MSRE geometry was simplified as shown in \cref{fig:real-vs-model}
+the actual \gls{MSRE} geometry was simplified as shown in \cref{fig:real-vs-model}
 where the actual geometry is on the left and the model geometry is on the
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{kophazi-actual-vs-model-core-geometry.png}
-  \caption{Left figure shows snapshot of actual MSRE core geometry; to satisfy
+  \caption{Left figure shows snapshot of actual \gls{MSRE} core geometry; to satisfy
     the 1D SCALE/CSAS/XSDRN code, the more regular geometry in the right figure
@@
 
-\subsection{ARFC MSRE Model Design Plan}
+\subsection{ARFC \gls{MSRE} Model Design Plan}
 
@@
 \item Test whether \code{gmsh} can generate heterogeneous 3D mesh structure
-  like that in the actual MSRE geometry.
+  like that in the actual \gls{MSRE} geometry.
 \item For expected range of temperatures and some defined sequence of
@@
 
-The most detailed report on ORNL's molten salt breeder reactor is the technical
+The most detailed report on \gls{ORNL}'s molten salt breeder reactor is the technical
 report by Robertson. \cite{robertson_conceptual_1971} A nice overview of the
@@
 
-	\[ C_{i,in}(t) = C_{i,out}(t- \tau_{EL})exp(- \lambda_i \tau_{EL}) \]
+	\[ C_{i,in}(t) = C_{i,out}(t- \tau_{EL})\exp(- \lambda_i \tau_{EL}) \]
 	\item \textit{Outlet boundary}. "Vacuum" condition for fast and thermal neutrons.

### 2016-10-06 MSR-design.tex
I'm fussy with my name on documents and I am happy as last author.
I find the red and green box links created by hyperref very distracting
kophazi gets a year

@@
 \usepackage{graphicx}
-\usepackage{hyperref}
+\usepackage[hidelinks]{hyperref}
 \usepackage{cleveref}
@@
 \title{Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design}
-\author{Alexander Lindsay, Katy Huff, Andrei Rykhlevskii} % As you author additions/changes, add
+\author{Alexander Lindsay, Andrei Rykhlevskii, Kathryn Huff} % As you author additions/changes, add
                                       % your name here!!!
@@
 bulk salt temperature (1175 \textdegree F). \cite{robertson_msre_1965} Some \gls{MSRE}
-modeling papers (\cite{kophazi_development_????}) refer to this down-flowing
+modeling papers (\cite{kophazi_development_2009}) refer to this down-flowing
 region as the \textit{downcomer}. The fuel salt is collected in the lower plenum
@@
 Kophazi developed a 3D time-dependent simulation that was validated against \gls{MSRE}
-data. \cite{kophazi_development_????} The model consists of a conventional
+data. \cite{kophazi_development_2009} The model consists of a conventional
 neutronics model extended to deal with the precursor drift that is unique to
@@
 with the last term representing the effect of fuel advection. In
-\cite{kophazi_development_????}, \cref{eq:neutrons} is solved only in the
+\cite{kophazi_development_2009}, \cref{eq:neutrons} is solved only in the
 reactor core, whereas \cref{eq:precursors} is solved both in the core and in the
@@
 with a volume equal to the total volume of all the external components and
-pipelines of the primary circuitry. \cite{kophazi_development_????} It is not
+pipelines of the primary circuitry. \cite{kophazi_development_2009} It is not
 entirely clear how pipe cross sectional areas are handled, which would determine
@@
 
-As pointed out in \cite{kophazi_development_????}, it is not possible to solve
+As pointed out in \cite{kophazi_development_2009}, it is not possible to solve
 \cref{eq:neutrons,eq:precursors} on the same mesh. \Cref{eq:neutrons} needs to
@@
 model from the real to effective geometry. Details of the discretization can be
-found in \cite{kophazi_development_????}. Unfortunately, neither
-\cite{kophazi_development_????} or cited references for the DALTON code,
+found in \cite{kophazi_development_2009}. Unfortunately, neither
+\cite{kophazi_development_2009} or cited references for the DALTON code,
 describe the boundary conditions used for neutrons.
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{kophazi_neutronics_discretization.png}
-  \caption{Homogenized model of fuel channels \cite{kophazi_development_????}}
+  \caption{Homogenized model of fuel channels \cite{kophazi_development_2009}}
   \label{fig:kophazi_homo}
@@
 through an axially varying heat transfer coefficient calculated with a Nusselt
-correlation; see \cite{kophazi_development_????} for details of the Nusselt
+correlation; see \cite{kophazi_development_2009} for details of the Nusselt
 correlation. Thermal expansion of the fuel was not accounted for while
@@
     the 1D SCALE/CSAS/XSDRN code, the more regular geometry in the right figure
-    is used \cite{kophazi_development_????}}
+    is used \cite{kophazi_development_2009}}
   \label{fig:real-vs-model}
@@
 thermal neutrons. More control rod modeling details can be found in
-\cite{kophazi_development_????}.
+\cite{kophazi_development_2009}.
 
@@
   \caption{Grid for cross section homogenization and neutron cross sections
-    \cite{kophazi_development_????}}
+    \cite{kophazi_development_2009}}
   \label{fig:neutron-grid}
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{cross-section-of-thermal-grid.png}
-  \caption{Cross-section of thermal grid \cite{kophazi_development_????}}
+  \caption{Cross-section of thermal grid \cite{kophazi_development_2009}}
   \label{fig:thermal-grid}
@@
       the cross sections similar to what is done in
-      \cite{kophazi_development_????}.
+      \cite{kophazi_development_2009}.
   \end{itemize}

### 2016-10-06 MSR-design.tex
include packages ordering is always complicated by hyperref
most style guides prefer the reference within the sentence (e.g. before the period).

@@
 \usepackage{graphicx}
-\usepackage[hidelinks]{hyperref}
-\usepackage{cleveref}
 \usepackage{textcomp}
@@
 \graphicspath{{./figures/}}
-
+% hyperref usually has to go last
+\usepackage[hidelinks]{hyperref}
+% but glossaries behaves best if after hyperref
 \usepackage[acronym,toc]{glossaries}
@@
 \makeglossaries
+% cleveref only behaves if after hyperref & glossaries
+\usepackage{cleveref}
 
@@
   \caption{Composition and properties of fuel, flush, and coolant
-    salts. \cite{robertson_msre_1965}}
+    salts \cite{robertson_msre_1965}.}
   \label{fig:salt_properties}
@@
 reactor vessel in a small annular region of 1 inch
-width. \cite{robertson_msre_1965} The fluid fuel then flows turbulently
+width \cite{robertson_msre_1965}. The fluid fuel then flows turbulently
 downward, cooling the reactor vessel to within 5\textdegree F of the entering
-bulk salt temperature (1175 \textdegree F). \cite{robertson_msre_1965} Some \gls{MSRE}
+bulk salt temperature (1175 \textdegree F) \cite{robertson_msre_1965}. Some \gls{MSRE}
 modeling papers (\cite{kophazi_development_2009}) refer to this down-flowing
@@
 2-inch square cross sections. Nominal core volume is 90 ft$^3$, with 70 ft$^3$
-occupied by graphite and 20 ft$^3$ occupied by fuel. \cite{robertson_msre_1965}
+occupied by graphite and 20 ft$^3$ occupied by fuel \cite{robertson_msre_1965}.
 After flowing through the core channels, the fuel collects in the upper plenum
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{MSRE_reactor_vessel.png}
-  \caption{\gls{MSRE} reactor vessel. \cite{robertson_msre_1965}}
+  \caption{\gls{MSRE} reactor vessel \cite{robertson_msre_1965}.}
   \label{fig:MSRE_reactor}
@@
 ($\Delta$k/k)/\textdegree F depending on the choice of
-fuel. \cite{robertson_msre_1965} The \gls{MSRE}'s three control rods have a combined
+fuel \cite{robertson_msre_1965}. The \gls{MSRE}'s three control rods have a combined
 worth of 5.6 - 7.6 \% $\Delta$k/k, again depending on the
-fuel. \cite{robertson_msre_1965}
+fuel \cite{robertson_msre_1965}.
 
@@
   \caption{Losses in reactivity associated with different
-    phenomena. \cite{robertson_msre_1965}}
+    phenomena \cite{robertson_msre_1965}.}
   \label{fig:reactivity_losses}
@@
 Kophazi developed a 3D time-dependent simulation that was validated against \gls{MSRE}
-data. \cite{kophazi_development_2009} The model consists of a conventional
+data \cite{kophazi_development_2009}. The model consists of a conventional
 neutronics model extended to deal with the precursor drift that is unique to
@@
 with a volume equal to the total volume of all the external components and
-pipelines of the primary circuitry. \cite{kophazi_development_2009} It is not
+pipelines of the primary circuitry \cite{kophazi_development_2009}. It is not
 entirely clear how pipe cross sectional areas are handled, which would determine
@@
 The most detailed report on \gls{ORNL}'s molten salt breeder reactor is the technical
-report by Robertson. \cite{robertson_conceptual_1971} A nice overview of the
+report by Robertson \cite{robertson_conceptual_1971}. A nice overview of the
 MSBR geometry is shown in \cref{fig:vertical,fig:horizontal,fig:zoom_horiz}.
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{Cammi_simplification_1.png}
-  \caption{Cammi's simplification of MSBR's geometry. \cite{cammi_multi-physics_2011}}
+  \caption{Cammi's simplification of MSBR's geometry 
+        \cite{cammi_multi-physics_2011}.}
   \label{fig:simlification}
@@
   \includegraphics[max height=.5\textheight,max width=\textwidth,keepaspectratio]{Cammi_simplification_2.png}
-  \caption{(b) Fluid flow and heat transfer boundary conditions; (c) neutron flux and DNP boundary conditions. \cite{cammi_multi-physics_2011}}
+  \caption{(b) Fluid flow and heat transfer boundary conditions; (c) neutron 
+        flux and DNP boundary conditions \cite{cammi_multi-physics_2011}.}
   \label{fig:simlification-2}

### 2016-10-06 MSR-design.tex
I've never heard this part of the reactor called anything except the 'downcomer'
neutron mesh -> neutronics mesh

@@
 downward, cooling the reactor vessel to within 5\textdegree F of the entering 
-bulk salt temperature (1175 \textdegree F) \cite{robertson_msre_1965}. Some \gls{MSRE}
-modeling papers (\cite{kophazi_development_2009}) refer to this down-flowing
-region as the \textit{downcomer}. The fuel salt is collected in the lower plenum
-(lower \textit{space}) of the reactor where straightening vanes remove the
-salt's rotational motion. The salt then flows upward through approximately 1140
-0.4-inch by 1.2-inch fuel channels that are formed by machining grooves in the
-sides of the graphite moderator columns \cite{robertson_msre_1965}; these are the
-regions where fission occurs. The graphite columns themselves have 2-inch by
-2-inch square cross sections. Nominal core volume is 90 ft$^3$, with 70 ft$^3$
-occupied by graphite and 20 ft$^3$ occupied by fuel \cite{robertson_msre_1965}.
+bulk salt temperature (1175 \textdegree F) \cite{robertson_msre_1965}. This 
+down-flowing region is typically referred to as the \textit{downcomer}. The 
+fuel salt is collected in the lower plenum (lower \textit{space}) of the 
+reactor where straightening vanes remove the salt's rotational motion. The salt 
+then flows upward through approximately 1140 0.4-inch by 1.2-inch fuel channels 
+that are formed by machining grooves in the sides of the graphite moderator 
+columns \cite{robertson_msre_1965}; these are the regions where fission occurs. 
+The graphite columns themselves have 2-inch by 2-inch square cross sections. 
+Nominal core volume is 90 ft$^3$, with 70 ft$^3$ occupied by graphite and 20 
+ft$^3$ occupied by fuel \cite{robertson_msre_1965}.
 After flowing through the core channels, the fuel collects in the upper plenum
@@
 general, the thermal grid is finer than the neutron grid. Thermal and neutronic
-calculations are coupled in the following way. Each cell of the neutron mesh
+calculations are coupled in the following way. Each cell of the neutronics mesh
 (containing both fuel and moderator, recall \cref{fig:kophazi_homo}) is

### 2016-10-06 MSR-design.tex
note about ultimate coupling goal.

@@
 
-The basis for this quick synopsis comes from \cite{wiki:Molten_salt_reactor}. 
+The basis for this quick synopsis comes from \cite{wikipedia_molten_2016}. 
 Research into \glspl{MSR} began in earnest with the \gls{ARE}, with experiments 
@@
             opposed to a non-linear variable that is a function of temperature.
+    \item However, the natural convection impacts on salt flow will 
+            significantly contribute to reactor dynamics and the ultimate goal 
+            will be to couple neutron flux and flow directly via 
+            temperature.
     \item We will need to decide whether neutron and temperature calculations

### 2016-10-19 MSR-design.tex
Add MSRE fuel salt, coolant salt, and graphite operating temperatures.

@@
 
-\title{Advanced Reactor Fuel Cycle (ARFC) Molten Salt Reactor Design}
+\title{Advanced Reactor Fuel Cycles Molten Salt Reactor Design}
 \author{Alexander Lindsay, Andrei Rykhlevskii, Kathryn Huff} % As you author additions/changes, add
@@
 
+The melting point of FLiBe is 459 \textdegree C and the boiling point is 1430
+\textdegree C \cite{_flibe_2016}.
+
 \subsection{Layout \& Equipment}
@@
 \subsubsection{Reactor vessel}
+\label{sec:reactor}
 
-A cutaway diagram of the \gls{MSRE} reactor is shown in \cref{fig:MSRE_reactor}. Fuel
-enters through the inlet and is distributed evenly along the outside of the
-reactor vessel in a small annular region of 1 inch
+A cutaway diagram of the \gls{MSRE} reactor is shown in
+\cref{fig:MSRE_reactor}. Fuel enters through the inlet and is distributed evenly
+along the outside of the reactor vessel in a small annular region of 1 inch
 width \cite{robertson_msre_1965}. The fluid fuel then flows turbulently
@@
 bulk salt temperature (1175 \textdegree F) \cite{robertson_msre_1965}. This
-down-flowing region is typically referred to as the \textit{downcomer}. The 
-fuel salt is collected in the lower plenum (lower \textit{space}) of the 
-reactor where straightening vanes remove the salt's rotational motion. The salt 
-then flows upward through approximately 1140 0.4-inch by 1.2-inch fuel channels 
-that are formed by machining grooves in the sides of the graphite moderator 
-columns \cite{robertson_msre_1965}; these are the regions where fission occurs. 
-The graphite columns themselves have 2-inch by 2-inch square cross sections. 
+down-flowing region is typically referred to as the \textit{downcomer}. The fuel
+salt is collected in the lower plenum (lower \textit{space}) of the reactor
+where straightening vanes remove the salt's rotational motion. The salt then
+flows upward through approximately 1140 0.4-inch by 1.2-inch fuel channels that
+are formed by machining grooves in the sides of the graphite moderator columns
+\cite{robertson_msre_1965}; these are the regions where fission occurs.  The
+graphite columns themselves have 2-inch by 2-inch square cross sections.
 Nominal core volume is 90 ft$^3$, with 70 ft$^3$ occupied by graphite and 20
-ft$^3$ occupied by fuel \cite{robertson_msre_1965}.
-After flowing through the core channels, the fuel collects in the upper plenum
-before exiting through the outlet.
+ft$^3$ occupied by fuel \cite{robertson_msre_1965}.  After flowing through the
+core channels, the fuel collects in the upper plenum before exiting through the
+outlet. At 10 MW, 0.6 MW of heat is generated in the graphite, 1.4 MW heat is
+generated in the fuel outside the nominal core, and 8.0 MW is generated in the
+fuel within the core \cite{robertson_msre_1965}. I'm very curious how those
+numbers were determined.
 
@@
 
+Flow in fuel channels is laminar; because both the graphite and fueld have good
+thermal conductivities, the maximum temperature of the graphite is only about 60
+\textdegree F above the mixed mean temperature of the adjacent fuel. Average and
+maximum temperatures of graphite are 1255 \textdegree F and 1300 \textdegree F
+respectively. The temperature of the fuel leaving the hottest channel in the
+core is about 1260 \textdegree F. The fuel leaves the top of the reactor at 7
+psig and an average temperature of 1225 \textdegree F \cite{robertson_msre_1965}.
+
 Though studies were conducted with the \gls{MSRE} core surrounded by varying
@@
 \cite{dulla_neutron_2004}.
+
+\subsubsection{Heat Exchanger}
+\label{sec:heatx}
+
+As mentioned in \cref{sec:reactor}, the fuel salt enters the reactor at 1175
+\textdegree F and leaves at 1225 \textdegree F. In order to cool the fuel salt
+back down to its reactor inlet temperature, the coolant salt flows through the
+heat exchanger at 850 \gls{gpm} with inlet and outlet temperatures of 1025
+\textdegree F and 1100 \textdegree F respectively \cite{robertson_msre_1965}.
 
@@
 distribution of delayed neutron production in the external primary circuit. That
-is a piece that would likely need to be included in detailed ARFC accident
+is a piece that would likely need to be included in detailed \gls{ARFC} accident
 models.
@@
 
-\subsection{ARFC \gls{MSRE} Model Design Plan}
+\subsection{\gls{ARFC} \gls{MSRE} Model Design Plan}
 
@@
 \FloatBarrier
-
+\clearpage
+\printglossary[type=\acronymtype]
 \bibliographystyle{unsrt}

### 2016-10-20 MSR-design.tex
Determine interpolation bounds and reference temps for fuel and moderator.

@@
 heat exchanger at 850 \gls{gpm} with inlet and outlet temperatures of 1025
-\textdegree F and 1100 \textdegree F respectively \cite{robertson_msre_1965}.
+\textdegree F and 1100 \textdegree F respectively \cite{robertson_msre_1965}. A
+summary of some of the important operating temperatures in the \gls{MSRE} is
+given in \cref{tab:important_temps}.
+
+\begin{table}[htpb]
+    \begin{center}
+      \begin{tabular}{l|c|c}
+        Material \& Location & Temp (\textdegree F) & Temp (K) \\
+        \hline \hline
+        Fuel salt reactor inlet/heatx outlet         & 1175 & 908  \\
+        Fuel salt reactor average outlet/heatx inlet & 1225 & 936  \\
+        Fuel salt reactor max outlet                 & 1260 & 955  \\
+        Coolant salt heatx inlet                     & 1025 & 825  \\
+        Coolant salt heatx outlet                    & 1100 & 866  \\
+        FLiBe boiling point                          & 2606 & 1703 \\
+        Graphite core average                        & 1255 & 953  \\
+        Graphite core maximum                        & 1300 & 978  \\
+      \end{tabular}
+    \end{center}
+    \caption{Some important operating temperatures in the \gls{MSRE}}
+    \label{tab:important_temps}
+\end{table}
+
+Based on the operating temperatures in \cref{tab:important_temps}, initial
+interpolation tables will range from 824 to 1055 K for the fuel salt
+temperature, and from 858 to 1088 K for the moderator temperature. The minimum
+fuel salt temperature is equal to the heat exchanger inlet coolant salt
+temperature, while the maximum fuel salt temperature is 100 K greater than the
+maximum fuel salt core outlet temperature. The moderator limits are 60
+\textdegree F greater than their fuel counterparts based on the experimental
+observation by Robertson that moderator temperatures are only ever about 60
+\textdegree F above the adjacent fuel. Reference temperatures for the fuel and
+moderator will be 922 K (the average of reactor inlet and outlet temperatures)
+and 953 K (graphite core average) respectively. These simulation set-points are
+summarized in \cref{tab:sim_temps}.
+
+\begin{table}[htpb]
+    \begin{center}
+      \begin{tabular}{l|c}
+        Serpent Simulation Temperatures & Value (K)\\
+        \hline \hline
+        Fuel minimum        & 824 \\
+        Fuel maximum        & 1055 \\
+        Fuel reference      & 922 \\
+        Moderator minimum   & 858 \\
+        Moderator maximum   & 1088 \\
+        Moderator reference & 953 \\
+      \end{tabular}
+    \end{center}
+    \caption{Relevant temperature parameters for Serpent simulations}
+    \label{tab:sim_temps}
+\end{table}
 

### 2017-01-05 MSR-design.tex
Update MSRE/MSBR material compositions.

@@
     \label{tab:important_temps}
-\end{table}
-
-Based on the operating temperatures in \cref{tab:important_temps}, initial
-interpolation tables will range from 824 to 1055 K for the fuel salt
-temperature, and from 858 to 1088 K for the moderator temperature. The minimum
-fuel salt temperature is equal to the heat exchanger inlet coolant salt
-temperature, while the maximum fuel salt temperature is 100 K greater than the
-maximum fuel salt core outlet temperature. The moderator limits are 60
-\textdegree F greater than their fuel counterparts based on the experimental
-observation by Robertson that moderator temperatures are only ever about 60
-\textdegree F above the adjacent fuel. Reference temperatures for the fuel and
-moderator will be 922 K (the average of reactor inlet and outlet temperatures)
-and 953 K (graphite core average) respectively. These simulation set-points are
-summarized in \cref{tab:sim_temps}.
-
-\begin{table}[htpb]
-    \begin{center}
-      \begin{tabular}{l|c}
-        Serpent Simulation Temperatures & Value (K)\\
-        \hline \hline
-        Fuel minimum        & 824 \\
-        Fuel maximum        & 1055 \\
-        Fuel reference      & 922 \\
-        Moderator minimum   & 858 \\
-        Moderator maximum   & 1088 \\
-        Moderator reference & 953 \\
-      \end{tabular}
-    \end{center}
-    \caption{Relevant temperature parameters for Serpent simulations}
-    \label{tab:sim_temps}
 \end{table}
@@
 
+\subsection{\gls{ARFC} \gls{MSRE} Model Design Execution}
+
+\subsubsection{Interpolation table generation}
+
+Based on the operating temperatures in \cref{tab:important_temps}, initial
+interpolation tables will range from 824 to 1055 K for the fuel salt
+temperature, and from 858 to 1088 K for the moderator temperature. The minimum
+fuel salt temperature is equal to the heat exchanger inlet coolant salt
+temperature, while the maximum fuel salt temperature is 100 K greater than the
+maximum fuel salt core outlet temperature. The moderator limits are 60
+\textdegree F greater than their fuel counterparts based on the experimental
+observation by Robertson that moderator temperatures are only ever about 60
+\textdegree F above the adjacent fuel. Reference temperatures for the fuel and
+moderator will be 922 K (the average of reactor inlet and outlet temperatures)
+and 953 K (graphite core average) respectively. These simulation set-points are
+summarized in \cref{tab:sim_temps}.
+
+\begin{table}[htpb]
+    \begin{center}
+      \begin{tabular}{l|c}
+        Serpent Simulation Temperatures & Value (K)\\
+        \hline \hline
+        Fuel minimum        & 824 \\
+        Fuel maximum        & 1055 \\
+        Fuel reference      & 922 \\
+        Moderator minimum   & 858 \\
+        Moderator maximum   & 1088 \\
+        Moderator reference & 953 \\
+      \end{tabular}
+    \end{center}
+    \caption{Relevant temperature parameters for Serpent simulations}
+    \label{tab:sim_temps}
+\end{table}
+
+The fuel salt density dependence on temperature is based on the \gls{FLiBe}
+density correlation in \cite{serrano-lopez_molten_2013}:
+
+\begin{equation}
+  \label{eq:flibe_density}
+  \rho(kg/m^3) = 2413.03-0.4884\cdot T(K)
+\end{equation}
+
+This does not account for the change in density introduced by dissolution of
+fuel components in the salt. At the average fuel salt temperature in the
+reactor, the \gls{FLiBe} correlation predicts a density of 1.96
+grams/cm$^3$. This differs from the measured values in the \gls{MSRE} of 2.24,
+2.08, and 2.14 grams/cm$^3$ for thorium-uranium, highly-enriched uranium, and
+partially-enriched uranium fuel salts respectively. Moderator density is
+currently considered to be constant and equal to 1.843 grams/cm$^3$
+\cite{cammi_multi-physics_2011}.
+
+Group constants required for eigenvalue calculation:
+
+\begin{equation}
+  \label{eq:constants}
+  D_g,\Sigma_{rg},\Sigma_{sg'g},\chi_g,\nu_g\Sigma_{fg},\kappa
+\end{equation}
+
+Additionally, $v_g$ is required for transient calculations.
+
 \section{MSBR}
